### 2022-08-06 paper/Chapters/Chapter02.tex
update paper

Due to the different of data structures, the point clouds can be grouped into types, structured point cloud based and unstructured point cloud based. The first case contains the neighbor information of each point together with a depth map or RGB image, the second case does not contain any neighbor information which has to be further calculated.

\paragraph{ Structured Point Cloud Based}
The relevant methods derive the surface normals based on spatial relationship, which utilizes the neighbor information for estimation. These methods performs well with a well-chosen window size. However, the drawbacks are that the algorithm is highly noise sensitive. It is weak in handling missing pixels, which is a common issue in the input data. The earlier methods usually use optimized methods. \cite{Holzer.S} proposed method to use local neighbors with an interest parameter $ p $ and compute the eigenvectors of the corresponding covariance matrix. They also smooth the depth data in order to handle the noise of depth image. The drawbacks are, as mentioned in the paper, the normals error go up when point depths change severely.  \cite{optimized-methods} did a comparison among the optimization-based methods.

@@

\paragraph{Depth Based}
Depth map contains the spatial information of the object surface, which is very important for the normal inference task. However, the depth map captured by depth sensors are usually with missing pixels and holes on dark, shinny or transparent regions.(\cite{nyu}). To overcome the missing pixels,
\cite{depth-inpainting-distribution} proposed a depth hole filling method using the depth distributions of neighboring regions.  \cite{nconv} introduced normalized convolution dealing with missing or uncertain data for convolution operation. It uses a binary mask to distinguish missing data and integrate it into the convolution operation. \cite{ncnn} applied it and use normalized convolution layers in their networks, which aims to reconstruct the missing pixels from the sparse depth map sensed by cameras. \cite{pncnn} proposed an input confidence estimation network to estimate the confidence instead of using a binary mask. However, the relevant papers are only using 1 channel data as model input, which didn't discussed the case for the multiple-channel data as input, such as RGB image, or structured point cloud.
\cite{depth-enhance-guided} further integrated RGB image as the guidance to deal with the missing pixels in the depth map.

@@

>>>>

%% depth map approach
Surface normal inference is a widely researched topic and can be solved in multiple directions. Based on a structured point cloud, the surface normal can be derived from geometry information of the point cloud, which mainly utilizes the neighbor information and consider it as an optimization problem (\cite{optimized-methods} ). They can perform well on dense point cloud input data based on a well-chosen window size. However, the drawbacks are that the algorithms are highly noise sensitive. 
The point cloud is usually not fully dense and normally converted from depth map, which are usually with missing pixels and holes on dark, shinny or transparent regions (\cite{nyu}). The missing points destabilizes the geometry based solution. To ease this problem, \cite{Holzer.S} proposed method to use local neighbors with an interest parameter $ p $ and compute the eigenvectors of the corresponding covariance matrix, which is used to smooth the depth data in order to handle the noise of depth image.  \cite{depth-inpainting-distribution} proposed an approach considers the depth distributions of neighboring regions to fill the holes in the depth map. 
Some approaches use deep learning method to fill missing areas. \cite{nconv} introduces normalized convolution to deal with missing or uncertain depth data with an added mask on the standard convolution operation. \cite{ncnn} applied it and use it as normalized convolution layers in their networks, which aims to reconstruct the missing pixels from the sparse depth map sensed by cameras. \cite{pncnn} proposed an input confidence estimation network to estimate the confidence instead of using a binary mask.

%% photometric approach
Photometric stereo is another approach that infer surface normal from BRDF based surface model. The surface normal is related with observed intensity, the incoming light direction, the outgoing viewing direction and the light intensity. It required multiple light conditions to get an optimal solution.

%% fusion approach

%% talk about gated convolution, Unet

%% in summary

@@

@@

\cite{depth-enhance-guided} further integrated RGB image as the guidance to deal with the missing pixels in the depth map.

### 2022-08-06 paper/Chapters/Chapter04.tex
update paper

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/08.pergolesi-side-chair_texture.png}
		\caption{chair}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/42.zebra_texture.png}
		\caption{zebra}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/01.bus_texture.png}
		\caption{bus}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/03.baoshanlu_texture.png}
		\caption{baoshanlu}
	\end{subfigure}

	\label{fig:dataset-demo}
	\caption{Point clouds scanned by high resolution scanners}
\end{figure}

@@

During the data collection, the object is randomly selected and placed on the stage. The object has a random upto 30 degrees rotation align $ roll $-axis, 30-degrees rotation align $ pitch $-axis and 180-degrees align $ yaw $-axis. Thus the camera has the opportunity to capture every direction of the object and consequently abundant the dataset. The layout in the Unity game engine is shown in Figure \ref{fig:unity-workplace}. We generate 3000 scenes with resolution $ 128\times128\times3 $ and 5000 scenes with resolution $ 512\times512\times3 $.

\begin{figure}[h!]
	\centering
	\includegraphics[width=.99\textwidth]{./Figures/unity-workplace.PNG}
	\caption{The layout of synthetic scenes generation in Unity.}
	\label{fig:unity-workplace}
\end{figure}

The main advantage using generated scenes is the availability of complete information. The depth map can be captured in a loss-free way. The corresponding normal map can also be safely considered as ground truth. And the scale of the dataset is easy to control. Table \ref{tab:data-files} gives more dataset information.
\begin{table}
	\caption{The information saved for each scene in ``synthetic50-5".}
	\label{tab:data-files}
	\centering
	\begin{tabular}{l l}
		\tabhead{Data} & \tabhead{Size} \\
		Depth map & Width$ \times $Height$ \times $ 1 \\
		\hline 
		Depth range  & MinDepth, MaxDepth \\  
		\hline
		Grayscale Image	&  Width$ \times $Height$ \times $ 1 \\  
		\hline 
		Normal Map &   Width$ \times $Height$ \times $ 3  \\
		\hline 
		Light Position &  $ 3\times1 $  \\
		\hline
		Camera Intrinsic Matrix &  $ 3\times 3 $  \\
		\hline 
		Camera Extrinsic Matrix &  $ 3\times 4 $  \\
		\hline 
	\end{tabular}
\end{table}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{./Figures/wrong_exposure_2.png}
		\caption{Too dim}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{./Figures/right_exposure.png}
		\caption{Just Right}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{./Figures/wrong_exposure.png}
		\caption{Too bright}
	\end{subfigure}
	\caption{Different exposure to the objects.}
	\label{fig:camera_exposure}
\end{figure}

@@

The grayscale image can be used as guided normal inference task and also as a readable scene for human. Since the image captured by camera is RGB format, we need to convert it to gray-color for our models. It based on following equation
\[ gray: \frac{r+2g+b}{4}  \]

@@

\begin{figure}[h!]
	\centering
	\begin{tikzpicture} 
		% reference lines
		\draw[thick,dashed]	(0,0) -- (10,0) ; % bottom
		\draw[thick,dashed]	(0,3) -- (10,3) node[pos=0.9, above] {image plane}; % middle
		\draw[thick,dashed]	(0,6) -- (10,6); % top
		% camera 
		\filldraw[black] (5,0) circle (2pt) node[anchor=south west]{Camera Position};
		% world point 
		\filldraw[black] (7,6) circle (2pt) node[anchor=north west]{Point};
		% image point
		\filldraw[black] (6,3) circle (2pt) node[anchor=north west]{Pixel};
		% similiar triangles
		\draw[thick] (5,0) -- (5,6); % AB
		\draw[thick] (5,0) -- (7,6); % AC
		\draw[thick] (5,6) -- (7,6) node[midway, below] {$ X $}; % BC
		\draw[thick] (5,3) -- (6,3) node[midway, below] {$ u $};
		% measure arrows
		\draw[thick, <->] (4,0) -- (4,3) node[midway, left] {$ fk_u $};
		\draw[thick, <->] (3,0) -- (3,6) node[pos=0.3, left] {$ Z $};
	\end{tikzpicture}	
	\caption{Convert depth to point in camera coordinate system}
	\label{fig:depth-triangulation}
\end{figure}

@@

\begin{figure}[!h]
	\centering
	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Extreme.png}}
	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Range.png}}
	\label{fig:data_range}
	\caption{Left: Extreme value in 3 axis; Right: Vertex range in 3 axis}
\end{figure}

\begin{table}[h!]
	\caption{ The fluctuation of extreme values and their ranges in 100 random training items. 
	}
	\label{tab:data-range}
	\centering
	\begin{tabular}{c | c c c}
		\hline 
		\tabhead{Axis} & \tabhead{Scale} & \tabhead{Min} & \tabhead{Max}\\
		\hline 
		X & 1.48 & -0.75 & 0.73\\
		\hline 
		Y & 1.56 & -0.76 & 0.80\\
		\hline 
		Z & 1.47 & 6.53 & 8.00\\
		\hline

	\end{tabular}
\end{table}

\subsection{Noise}
\label{sec:noise}
The raw depth maps captured by light scanner usually have missing pixels. In order to fit well with real-data, the synthetic data has been added uniform distributed noise, which is randomly remove the valid pixels in the maps.
The simulated noise is distributed evenly around the whole map with a specific noise intensity. A parameter $ \mu $ is used to control the intensity of noise, it denotes the $ \mu $-percent pixel dropoff. For example, $ \mu-10 $ removes 10\% pixels randomly. For each scene, the noising operation based on a random $ \mu $ in a range $ \left[0, 50\right]  $ is used. Some scenes have more missing pixels and some have less. The random noise intensity also enables the model to learn scenarios not only with noise, but also with minor noise or even without noise.
Figure \ref{fig:noise-intensity} shows the noise effect with different $ \mu $.
%% add noise image
\begin{figure}[!h]
	\centering
	{\includegraphics[width=.9\textwidth]{./Figures/add_noise_depth.png}}
	\caption{Noise-intensity on $ \mu-0, \mu-10,\mu-20, \mu-30, \mu-40, \mu-50,$. Object Name: elephant-zun-lid.}
	\label{fig:noise-intensity}
\end{figure}

\subsection{Fit to PyTorch}
In order to saving the training time, the dataset is compressed in PyTorch format. The structure of a single item is shown in Table \ref{tab:tensor-structure}.
\begin{table}[H]
	\caption{The structure of a single tensor in the dataset.}
	\label{tab:tensor-structure}
	\centering
	\begin{tabular}{l | l}
		\tabhead{Name} & \tabhead{Content} \\
		\multirow{3}{*}{input-tensor}  & Vertex \\  & Image \\  & Light Direction \\
		\hline
		\multirow{3}{*}{output-tensor}  & GT-Normal \\ & Image \\ & GT-Light-Direction \\
		\hline
		Light position & light position \\
		\hline 
		Camera Matrix  & K,R,t\\
		\hline 
		Depth Range  & minDepth, maxDepth\\
	\end{tabular}
\end{table}

>>>>

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/08.pergolesi-side-chair_texture.png}
		\caption{chair}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/train-dataset/42.zebra_texture.png}
		\caption{zebra}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/01.bus_texture.png}
		\caption{bus}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test-dataset/03.baoshanlu_texture.png}
		\caption{baoshanlu}
	\end{subfigure}
	\decoRule
	\label{fig:dataset-demo}
	\caption{Point clouds scanned by high resolution scanners}
\end{figure}

@@

During the data collection, the object is randomly selected and placed on the stage. The object has a random upto 30 degrees rotation align $ roll $-axis, 30-degrees rotation align $ pitch $-axis and 180-degrees align $ yaw $-axis. Thus the camera has the opportunity to capture every direction of the object and consequently abundant the dataset. The layout in the Unity game engine is shown in Figure \ref{fig:unity-workplace}. We generate 3000 scenes with resolution $ 128\times128 $ and 5000 scenes with resolution $ 512\times512 $.

\begin{figure}[h!]
	\centering
	\includegraphics[width=.99\textwidth]{./Figures/unity-workplace.PNG}
	\decoRule
	\caption{The layout of synthetic scenes generation in Unity.}
	\label{fig:unity-workplace}
\end{figure}

The main advantage using generated scenes is the availability of complete information. The depth map can be captured in a loss-free way. The corresponding normal map can also be safely considered as ground truth. And the scale of the dataset is easy to control. Table \ref{tab:data-files} gives more dataset information.
\begin{table}
	\caption{The information saved for each scene in ``synthetic50-5".}
	\label{tab:data-files}
	\centering
	\begin{tabular}{l l}
		\toprule
		\tabhead{Data} & \tabhead{Size} \\
		\midrule
		Depth map & Width$ \times $Height$ \times $ 1 \\
		\hline 
		Depth range  & MinDepth, MaxDepth \\  
		\hline
		Grayscale Image	&  Width$ \times $Height$ \times $ 1 \\  
		\hline 
		Normal Map &   Width$ \times $Height$ \times $ 3  \\
		\hline 
		Light Position &  $ 3\times1 $  \\
		\hline
		Camera Intrinsic Matrix &  $ 3\times 3 $  \\
		\hline 
		Camera Extrinsic Matrix &  $ 3\times 4 $  \\
		\hline 
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{./Figures/wrong_exposure_2.png}
		\caption{Too dim}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{./Figures/right_exposure.png}
		\caption{Just Right}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{./Figures/wrong_exposure.png}
		\caption{Too bright}
	\end{subfigure}
	\decoRule
	\caption{Different exposure to the objects.}
	\label{fig:camera_exposure}
\end{figure}

@@

The grayscale image can be used as guided normal inference task and also as a readable scene for human. Since the image captured by camera is RGB format, we need to convert it to gray-color for our models. It based on following equation
\[ gray: \frac{R+2G+B}{4}  \]

@@

\begin{figure}[h!]
	\centering
	\begin{tikzpicture} 
		% reference lines
		\draw[thick,dashed]	(0,0) -- (10,0) ; % bottom
		\draw[thick,dashed]	(0,3) -- (10,3) node[pos=0.9, above] {image plane}; % middle
		\draw[thick,dashed]	(0,6) -- (10,6); % top
		% camera 
		\filldraw[black] (5,0) circle (2pt) node[anchor=south west]{Camera Position};
		% world point 
		\filldraw[black] (7,6) circle (2pt) node[anchor=north west]{Point};
		% image point
		\filldraw[black] (6,3) circle (2pt) node[anchor=north west]{Pixel};
		% similiar triangles
		\draw[thick] (5,0) -- (5,6); % AB
		\draw[thick] (5,0) -- (7,6); % AC
		\draw[thick] (5,6) -- (7,6) node[midway, below] {$ X $}; % BC
		\draw[thick] (5,3) -- (6,3) node[midway, below] {$ u $};
		% measure arrows
		\draw[thick, <->] (4,0) -- (4,3) node[midway, left] {$ fk_u $};
		\draw[thick, <->] (3,0) -- (3,6) node[pos=0.3, left] {$ Z $};
	\end{tikzpicture}	
	\decoRule
	\caption{Convert depth to point in camera coordinate system}
	\label{fig:depth-triangulation}
\end{figure}

@@

\begin{figure}[!h]
	\centering
	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Extreme.png}}
	{\includegraphics[width=0.45\textwidth]{./Figures/Data_Range.png}}
	\label{fig:data_range}
	\decoRule
	\caption{Left: Extreme value in 3 axis; Right: Vertex range in 3 axis}
\end{figure}

\begin{table}[th]
	\label{tab:data-range}
	\centering
	\begin{tabular}{c | c c c}
		\toprule
		\tabhead{Axis} & \tabhead{Scale} & \tabhead{Min} & \tabhead{Max}\\
		\midrule
		X & 1.48 & -0.75 & 0.73\\
		\hline 
		Y & 1.56 & -0.76 & 0.80\\
		\hline 
		Z & 1.47 & 6.53 & 8.00\\
		\bottomrule

	\end{tabular}
	\caption{ The fluctuation of extreme values and their ranges in 100 random training items. }
\end{table}

\subsection{Noise}
\label{sec:noise}
The raw depth maps captured by light scanner usually have missing pixels. In order to fit well with real-data, the synthetic data has been added uniform distributed noise, which is randomly remove the valid pixels in the maps.
The simulated noise is distributed evenly around the whole map with a specific noise intensity. A parameter $ \mu $ is used to control the intensity of noise, it denotes the $ \mu $-percent pixel dropoff. For example, $ \mu-10 $ removes 10\% pixels randomly. For each scene, the noising operation based on a random $ \mu $ in a range $ \left[0, 50\right]  $ is used. Some scenes have more missing pixels and some have less. The random noise intensity also enables the model to learn scenarios not only with noise, but also with minor noise or even without noise.
Figure \ref{fig:noise-intensity} shows the noise effect with different $ \mu $.
%% add noise image
\begin{figure}[!h]
	\centering
	{\includegraphics[width=.9\textwidth]{./Figures/add_noise_depth.png}}
	\decoRule
	\caption{Noise-intensity on $ \mu-0, \mu-10,\mu-20, \mu-30, \mu-40, \mu-50,$. Object Name: elephant-zun-lid.}
	\label{fig:noise-intensity}
\end{figure}

\subsection{Fit to PyTorch}
In order to saving the training time, the dataset is compressed in PyTorch format. The structure of a single item is shown in Table \ref{tab:tensor-structure}.
\begin{table}[H]
	\caption{The structure of a single tensor in the dataset.}
	\label{tab:tensor-structure}
	\centering
	\begin{tabular}{l | l}
		\toprule
		\tabhead{Name} & \tabhead{Content} \\
		\midrule
		\multirow{3}{*}{input-tensor}  & Vertex \\  & Image \\  & Light Direction \\
		\hline
		\multirow{3}{*}{output-tensor}  & GT-Normal \\ & Image \\ & GT-Light-Direction \\
		\hline
		Light position & light position \\
		\hline 
		Camera Matrix  & K,R,t\\
		\hline 
		Depth Range  & minDepth, maxDepth\\
		\bottomrule
	\end{tabular}
\end{table}

### 2022-08-06 paper/Chapters/Chapter05.tex
update paper

The performance of neighbor based method is good enough for a well chosen $ k $. However, for the case of noised point cloud as input, this approach will broken, since the noise will failed the neighbor assumption and also reduce the number of possible neighbors of each point for a fixed $ k $.
\begin{figure}[th]
	\centering
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_point_cloud_noise.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_groundtruth.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_normal_SVD.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_error_SVD.png}	
	\decoRule
	\label{fig:svd-noise}
	\caption{Evaluation of neighbor based method on a noised dragon model}
\end{figure}

@@

	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Normal inference based on GCNN. ($ 128\times128 $)}
	\label{fig:gcnn-eval}
\end{figure}

@@

	\decoRule
	\caption{Zoom in of some regions of Dragon object (GCNN models). Zoom-in normal map corresponding $ 32\times32 $ points in the original matrix.}
	\label{fig:gcnn-eval-synthetic-zoom-in}
\end{figure}

@@

	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Normal inference based on Trip-Net. Test image has resolution $ 128\times128 $}
	\label{fig:trip-eval}
\end{figure}

@@

	\decoRule
	\caption{Comparison between different fusion times for Trip-Net. }
	\label{fig:tripnet-eval-synthetic-zoom-in}
\end{figure}

@@

	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Normal inference based on Trip-Net. Test image has resolution $ 128\times128 $}
	\label{fig:trip-eval-high-resolution}
\end{figure}

@@

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_SVD.png}
		\caption{SVD}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_NNNN-512.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_Trip-Net-512.png}
		\caption{Trip-Net}
	\end{subfigure}
	\decoRule
	\caption{High resolution dataset ($ 512\times 512 $) comparison.}
	\label{fig:trip-eval-compare}
\end{figure}

>>>>

The performance of neighbor based method is good enough for a well chosen $ k $. However, for the case of noised point cloud as input, this approach will broken, since the noise will failed the neighbor assumption and also reduce the number of possible neighbors of each point for a fixed $ k $.
\begin{figure}[th]
	\centering
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_point_cloud_noise.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_groundtruth.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_normal_SVD.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_error_SVD.png}	
	\decoRule
	\label{fig:svd-noise}
	\caption{SVD visual evaluation on a noised dragon model ($ 128\times128 $)}
\end{figure}

@@

	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{GCNN visual evaluation. Window size $ 128\times128 $}
	\label{fig:gcnn-eval}
\end{figure}

@@

	\decoRule
	\caption{Zoom in of some regions of Dragon object (GCNN models). Window size $ 32\times32 $.}
	\label{fig:gcnn-eval-synthetic-zoom-in}
\end{figure}

@@

	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Trip-Net visual evaluation on resolution $ 128\times128 $}
	\label{fig:trip-eval}
\end{figure}

@@

	\decoRule
	\caption{Comparison between different fusion times on Trip-Net Architecture ($ 128\times128 $). }
	\label{fig:tripnet-eval-synthetic-zoom-in}
\end{figure}

@@

	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Trip-Net visual evaluation on high resolution dataset $ 512 \times 512 $.}
	\label{fig:trip-eval-high-resolution}
\end{figure}

@@

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_SVD.png}
		\caption{SVD}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_NNNN-512.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_Trip-Net-512.png}
		\caption{Trip-Net}
	\end{subfigure}
	\decoRule
	\caption{Comparison on high resolution dataset ($ 512\times 512 $) .}
	\label{fig:trip-eval-compare}
\end{figure}

### 2022-08-06 paper/Chapters/Chapter06.tex
update paper

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
In our approaches, two networks have been proposed. The first network called GCNN is used for geometry information based approach, which is our baseline method. It is especially good for the semi-dense input data which is benefited with gated convolution layer design.  Using this network we achieved a more accurate normal inference than using standard layers network based on the same architecture. We also show the effectiveness of skip connection in the U-Net. Our network uses a fully convolution design which enables it takes any resolution images as input.

The second network is called Trip-Net, which is based on the GCNN model. It is designed for illumination calibrated RGB-D image based approaches. This model utilises GCNN architecture three times in order to handle vertex map, light map and image map separately. We have also found that 3 to 4 times fusion times among 3 pipes in our models is the key point for the performance enhancement.
Based on our experiments, we found that the models trained on illuminated calibrated RGB-D images achieve a  better performance than geometry information only based approach and gives more sharpness in the normal map.

@@

In our experiments we collected 55 high density point clouds from internet and used them for our dataset generation. Specifically, we use a RGB-D camera, an ambient light and one directional light  collect thousands of scenes. The scene generation is simulated by game engine Unity. Furthermore, we also simulated noise in our synthetic dataset by a uniform distributed drop off to fit our model adopt with semi-dense input data.

However, for the large missing areas, we did not generate a similar noise in the training set, which leads to our model cannot fill the holes in the real data. Exploring a sensor-noise mimic algorithm to generate more reality closed data for training work can be a direction of further work.

>>>>

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
In our approaches, two networks have been proposed. The first network called GCNN is used for geometry information based approach, which is our baseline method. It is especially good for the semi-dense input data which is benefited with gated convolution layer design.  Using this network we achieved a more accurate normal inference than using standard layers network based on the same architecture. We also show the effectiveness of skip connection in the U-Net. Besides, the fully convolution design enables it to use various resolution images as input.

The second network is called Trip-Net, which is based on the GCNN model. It is designed for illumination calibrated RGB-D image based approaches. This model utilises GCNN architecture three times in order to handle vertex map, light map and image map separately. We have also found that 3 to 4 times fusion times among 3 pipes in our models is the key point for the performance enhancement.
Based on our experiments, it shows that the models trained on illuminated calibrated RGB-D images achieve a  better performance than geometry information only based approach and gives more sharpness in the normal map.

@@

We collected 55 high density point clouds from internet and used them for our dataset generation. Specifically, we use a RGB-D camera, an ambient light and one directional light  collect thousands of scenes. The scene generation is simulated by game engine Unity. Furthermore, we also simulated noise in our synthetic dataset by a uniform distributed drop off to fit our model adopt with semi-dense input data.
However, for the large missing areas, we did not generate a similar noise in the training set, which leads to our model cannot fill the holes in the real data. Exploring a sensor-noise mimic algorithm to generate more reality closed data for training work can be a direction of further work.
